Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
more text and some fixes

\section{Related Work}
\label{sec:relatedwork}
    %TODO
    To be robust with respect to different recording conditions and speakers,
    one can either aim to adapt the model parameters to these new situations or
    to learn representations which are invariant to them.
    Unfortunately, many of the adaptation methods which have been designed for
    GMM-HMM systems cannot be applied to DNN-based systems. For this reason, a
    large body of recent work has investigated new adaptation methods for neural
    networks.

    The effectiveness of representations produced by a neural network for internal 
    noise reduction is discussed by~\cite{yu2013feature} and this work sets a 
    baseline for experiments on the Aurora-4 dataset.

    Some of the linear and affine transformations used for GMM adaptation can
    still be applied to neural networks when one limits these adaptations to the
    very last layer, as was shown in~ \cite{yao2012adaptation}. The
    improvements seemed to rely mostly on the adaptation of the bias parameters.

    Many neural network speaker/condition adaptation methods are based on
    i-vectors. One way to do this is by providing the i-vectors as additional
    inputs \cite{senior2014improving}.

    In the specific case of noise robustness, one can use speech enhancement to
    obtain more robust features and neural networks have been used for this for
    decades \cite{knecht1995neural}. A further step in this direction is to train
    systems to recognize speech and perform speech enhancement jointly \cite{narayanan2014joint}.

    Another strategy is to retrain the model parameters using a very small
    number of utterances from the new domain while making sure that the model
    doesn't stray too far away from the parameter values that were obtained from
    the train data \cite{yu2013kl}.
    The adaptation to new domains can also be kept under control by limiting
    the number of parameters which are adapted to the new data or by limiting the
    adaptation to a rescaling of the hidden unit activations
    \cite{swietojanski2014learning}.

    Recently, in a work by~\cite{yusuke2016adversarial} a multi-layer sigmoidal network was trained 
    in an adversarial fashion on an in-house transcription task corrupted by noise.

    %TODO
    \cite{saon2017english} use a form of adversarial training with a network
    that predicts an i-vector using the mean square error loss.

>>>>

\section{Related Work}
\label{sec:relatedwork}
    %TODO
    Neural networks display some robustness towards different recording
    conditions and speaker by themselves and the effectiveness of representations
    produced by a neural network for internal 
    noise reduction is discussed by~\cite{yu2013feature}. This work sets a 
    baseline for experiments on the Aurora-4 dataset.

    To be even more robust with respect to different recording conditions and speakers,
    one can either aim to adapt the model parameters to these new situations or
    to learn representations which are invariant to them.
    Most approaches so far, are based on adaptation.
    Unfortunately, many of the adaptation methods which have been designed for
    GMM-HMM systems cannot be applied to DNN-based systems. For this reason, a
    large body of recent work has investigated new adaptation methods for neural
    networks.

    Some of the linear and affine transformations used for GMM adaptation can
    still be applied to neural networks when one limits these adaptations to the
    very last layer, as was shown in~\cite{yao2012adaptation}. The
    improvements seemed to rely mostly on the adaptation of the bias parameters.
    A clear downside of this approach is that it doesn't utilize the
    representational power provided by the non-linear multi-layer structure of deep
    neural networks.

    Many neural network speaker adaptation methods are based on
    i-vectors. The most common way to exploit i-vectors is by providing them as additional
    inputs \cite{senior2014improving,saon2013speaker}. This means that i-vectors also need to
    be available during testing and this may not always be practical.

    In the specific case of noise robustness, one can use speech enhancement to
    obtain more robust features and neural networks have been used for this for
    decades \cite{knecht1995neural}. A further step in this direction is to train
    systems to recognize speech and perform speech enhancement jointly \cite{narayanan2014joint}. 
    We argue that speech enhancement is a more difficult task to learn than
    invariance to certain noise conditions and more likely to suffer from
    overfitting when the amount of available noisy data is limited.

    Another adaptation strategy is to retrain the model parameters using a very small
    number of utterances from the new domain while making sure that the model
    doesn't stray too far away from the parameter values that were obtained from
    the train data \cite{yu2013kl}.
    The adaptation to new domains can also be kept under control by limiting
    the number of parameters which are adapted to the new data or by limiting the
    adaptation to a rescaling of the hidden unit activations
    \cite{swietojanski2014learning}.
    The most important difference between these approaches and our work is that
    we don't adapt the model parameters at all after training. In many
    situations this may not be possible and retraining of models may require more
    from the hardware on which the speech recognition system is implemented.

    Recently, in a work by~\cite{yusuke2016adversarial} a multi-layer sigmoidal network was trained 
    in an adversarial fashion on an in-house transcription task corrupted by noise.
    This work is very similar to our approach but we evaluate our methods on
    more challenging benchmark while investigating different numbers of noise
    conditions. Our work also differs due to the use of more modern rectifier
    activation based classification networks.
    Finally, in other very recent work, \cite{saon2017english} a form of adversarial training with a network
    that predicts an i-vector using the mean square error loss was used.
